quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-08-18 paper-quollr.Rmd
Added the projections for linked plots

@@

scurve_proj_umap_model1_selected2 <- ggplot() +
      geom_point(
        data = projected_df,
        aes(
          x = proj1,
          y = proj2,
          colour = factor(cluster, levels = c("deselected", "selected")),
          size = factor(cluster, levels = c("deselected", "selected"))),
        alpha = 0.5) +
      geom_segment(
        data = model_df,
        aes(
          x = proj1_from,
          y = proj2_from,
          xend = proj1_to,
          yend = proj2_to),
        colour = "#000000",
        linewidth = 0.8,
        alpha = 0.4) +
      geom_segment(
          data=axes,
          aes(x=x1, y=y1, xend=x2, yend=y2),
          colour="grey70") +
        geom_text(
          data=axes,
          aes(x=x2, y=y2),
          label=rownames(axes),
          colour="grey50",
          size = 2.5) +
        geom_path(
          data=circle,
          aes(x=c1, y=c2), colour="grey70") +
        xlim(c(-0.35, 0.35)) +
        ylim(c(-0.35, 0.35)) +
  interior_annotation(label = "b2", cex = 1) +
  scale_color_manual(values = c(clr_choice, '#756bb1')) +
  scale_size_manual(values = c('deselected' = 1.0, 'selected' = 1.5)) +
  theme(aspect.ratio = 1,
        legend.position = "none")
```

@@

```{r, eval=knitr::is_latex_output()}
error_plot_scurve_hist1 + scurve_umap_plt_select1_lk2 + scurve_umap_plt_select1 +
  error_plot_scurve_hist2 + scurve_umap_plt_select2_lk2 + scurve_umap_plt_select1 +
  plot_layout(ncol = 3)
```

>>>>

scurve_proj_umap_model1_selected1_dp <- ggplot() +
      geom_point(
        data = projected_df,
        aes(
          x = proj1,
          y = proj2,
          colour = factor(cluster, levels = c("deselected", "selected")),
          size = factor(cluster, levels = c("deselected", "selected"))),
        alpha = 0.5) +
      geom_segment(
        data = model_df,
        aes(
          x = proj1_from,
          y = proj2_from,
          xend = proj1_to,
          yend = proj2_to),
        colour = "#000000",
        linewidth = 0.8,
        alpha = 0.4) +
      geom_segment(
          data=axes,
          aes(x=x1, y=y1, xend=x2, yend=y2),
          colour="grey70") +
        geom_text(
          data=axes,
          aes(x=x2, y=y2),
          label=rownames(axes),
          colour="grey50",
          size = 2) +
        geom_path(
          data=circle,
          aes(x=c1, y=c2), colour="grey70") +
        xlim(c(-0.35, 0.35)) +
        ylim(c(-0.35, 0.35)) +
  interior_annotation(label = "a3", cex = 1) +
  scale_color_manual(values = c(clr_choice, '#756bb1')) +
  scale_size_manual(values = c('deselected' = 1.0, 'selected' = 1.5)) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

scurve_proj_umap_model1_selected2 <- ggplot() +
      geom_point(
        data = projected_df,
        aes(
          x = proj1,
          y = proj2,
          colour = factor(cluster, levels = c("deselected", "selected")),
          size = factor(cluster, levels = c("deselected", "selected"))),
        alpha = 0.5) +
      geom_segment(
        data = model_df,
        aes(
          x = proj1_from,
          y = proj2_from,
          xend = proj1_to,
          yend = proj2_to),
        colour = "#000000",
        linewidth = 0.8,
        alpha = 0.4) +
      geom_segment(
          data=axes,
          aes(x=x1, y=y1, xend=x2, yend=y2),
          colour="grey70") +
        geom_text(
          data=axes,
          aes(x=x2, y=y2),
          label=rownames(axes),
          colour="grey50",
          size = 2.5) +
        geom_path(
          data=circle,
          aes(x=c1, y=c2), colour="grey70") +
        xlim(c(-0.35, 0.35)) +
        ylim(c(-0.35, 0.35)) +
  interior_annotation(label = "b2", cex = 1) +
  scale_color_manual(values = c(clr_choice, '#756bb1')) +
  scale_size_manual(values = c('deselected' = 1.0, 'selected' = 1.5)) +
  theme(aspect.ratio = 1,
        legend.position = "none")

scurve_proj_umap_model1_selected2_dp <- ggplot() +
      geom_point(
        data = projected_df,
        aes(
          x = proj1,
          y = proj2,
          colour = factor(cluster, levels = c("deselected", "selected")),
          size = factor(cluster, levels = c("deselected", "selected"))),
        alpha = 0.5) +
      geom_segment(
        data = model_df,
        aes(
          x = proj1_from,
          y = proj2_from,
          xend = proj1_to,
          yend = proj2_to),
        colour = "#000000",
        linewidth = 0.8,
        alpha = 0.4) +
      geom_segment(
          data=axes,
          aes(x=x1, y=y1, xend=x2, yend=y2),
          colour="grey70") +
        geom_text(
          data=axes,
          aes(x=x2, y=y2),
          label=rownames(axes),
          colour="grey50",
          size = 2) +
        geom_path(
          data=circle,
          aes(x=c1, y=c2), colour="grey70") +
        xlim(c(-0.35, 0.35)) +
        ylim(c(-0.35, 0.35)) +
  interior_annotation(label = "b3", cex = 1) +
  scale_color_manual(values = c(clr_choice, '#756bb1')) +
  scale_size_manual(values = c('deselected' = 1.0, 'selected' = 1.5)) +
  theme(aspect.ratio = 1,
        legend.position = "none")
```

@@

```{r, eval=knitr::is_latex_output()}
error_plot_scurve_hist1 + scurve_umap_plt_select1_lk2 + scurve_proj_umap_model1_selected1_dp +
  error_plot_scurve_hist2 + scurve_umap_plt_select2_lk2 + scurve_proj_umap_model1_selected2_dp +
  plot_layout(ncol = 3)
```
